---
title: "Testing spatial autocorrelation"
author: "Anna Stroh"
date: "2025-09-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Testing spatial autocorrelation in spatially-explicit delta models

## Preface

This vignette is demonstrating code to test spatial autocorrelation in sdmTMB 
models using global and local autocorrelation test which are applied to each
model predictor (i.e. binomial/lognormal).

The code is inspired by Cacciapaglia et al. (2024) Developing workflow and 
diagnostics for model selection of a vector autoregressive spatiotemporal (VAST) 
model in comparison to design-based indices. 
https://doi.org/10.1016/j.fishres.2024.107009.

I reverse engineered the code behind the plots and autocorrelation tests 
outlined in the publication. To ensure that the tests are accurately employed,
I checked with the literature on assessing spatial autocorrelation.

Since there are differences in model residuals with respect to their model 
predictor (i.e. binomial/log normal), I created and apply functions separately
to each model predictor. While I specified the functions to calculate metrics 
for residuals, we can easily swap that argument for other data that we are 
interested in, i.e. model estimate in predictions, or raw data.

## Load required packages

```{r}
library(dbscan) # for spatial clustering
library(spdep) # for autocorrelation tests
library(ggplot2); theme_set(theme_bw())

library(purrr) # iteration over lists

library(sdmTMB)
```
## Introduction

If present, spatial autocorrelation changes how trends across space are 
estimated, relative to the assumption of independence between points. 

Moran's I is a commonly used indicator of spatial autocorrelation. Initially 
developed by Moran (1948), the calculations were generalised and extended to 
spatial weights matrices by Cliff and Ord (1973). 


## Step 1: build spatial weights list using k nearest neighbour clustering

I am using the spdep package to calculate spatial autocorrelation metrics. To 
obtain these metrics, I need to create a spatial weights list, 
which defines the spatial relationships between observations—often based on 
distance or neighborhood structure. In this case, I clustered pairs of points
using k-nearest neighbours (KNN). KNN is recommended for irregularly spaced 
data and sparse data over large areas. Since I needed to remove a stratum due
to missing data, I have widely spaced data. KNN ensures full connectivity 
between points which is necessary for testing spatial correlation.

```{r}
make_kn_dist_obj_binom <- function(coords) {
  kn_dist_obj <- list()
  years <- unique(coords$year)
  max_k = 20
  # Note: spdep also allows distance-based clustering - I just went with k-based method 
  
  # helper function to find the smallest k with connected graph
  get_min_k_connected <- function(y_coords, label, y) {
    min_k <- list()
    crds <- cbind(y_coords$lon, y_coords$lat)
    
    for (k in 1:max_k) {
      crds <- cbind(y_coords$lon, y_coords$lat)
      knn <- knearneigh(crds, k = k) 
      nb <- knn2nb(knn)
      
      comps <- n.comp.nb(nb)
      
      if (comps$nc == 1) {
        # make and save graph-based k-nearest neighbour connections 
        plot(nb, crds, 
             main = paste("Connected KNN graph (", label, ", k =", k, ") in year", y))
        
        # make list symmetric - Moran's test assumes symmetry
        nb_sym <- make.sym.nb(nb)
        
        # create spatial weights list
        nblistw <- nb2listw(nb_sym)
        
        # save spatial weights list
        min_k[[1]] <- list(k = k, nb = nb_sym, nblistw = nblistw, 
                                           coordsdat = y_coords)
        break
        
      }
    }
    return(min_k)
  } 
  for (y in years) {
    y_coords <- subset(coords, year == y)
    binom <- y_coords[, c("year", "lon", "lat", "resids")]
    
    min_k_binom <- get_min_k_connected(binom, "binom", y)
    
    kn_dist_obj[[as.character(paste0("y", y))]] <- min_k_binom

  }
  return(kn_dist_obj)
}

make_kn_dist_obj_pos <- function(coords) {
  kn_dist_obj <- list()
  years <- unique(coords$year)
  max_k = 20
  
  # helper function to find the smallest k with connected graph
  get_min_k_connected <- function(y_coords, label, y) {
    min_k <- list()
    crds <- cbind(y_coords$lon, y_coords$lat)
    
    for (k in 1:max_k) {
      crds <- cbind(y_coords$lon, y_coords$lat)
      knn <- knearneigh(crds, k = k) 
      nb <- knn2nb(knn)
      
      comps <- n.comp.nb(nb)
      
      if (comps$nc == 1) {
        # make and save graph-based k-nearest neighbour connections 
        plot(nb, crds, 
             main = paste("Connected KNN graph (", label, ", k =", k, ") in year", y))
        
        # make list symmetric - Moran's test assumes symmetry
        nb_sym <- make.sym.nb(nb)
        
        # create spatial weights list
        nblistw <- nb2listw(nb_sym)
        
        # save spatial weights list
        min_k[[1]] <- list(k = k, nb = nb_sym, nblistw = nblistw, 
                                           coordsdat = y_coords)
        break
      }
    }
    return(min_k)
  } 
  
  for (y in years) {
    y_coords <- subset(coords, year == y)
    pos <- y_coords[, c("year", "lon", "lat", "resids2")]
    pos <- pos[! is.na(pos$resids2), ] # remove NAs
    
    min_k_pos <- get_min_k_connected(pos, "pos", y)
    
    kn_dist_obj[[as.character(paste0("y", y))]] <- min_k_pos
    
  }
  return(kn_dist_obj)
}

```

### Load example data

We use whiting data as an example and subset to age 0 group to estimate a simple
univariate model. 
```{r }
load(paste0(getwd(), "/whg_biomass_sdmTMB.RData"))
dat <- subset(dat, age == 0)
dat <- add_utm_columns(dat, c("lon", "lat"), units = "km") # CRS = 32629
mesh <- make_mesh(dat, c("X", "Y"), cutoff = 20) # simple mesh for example only
```

### Model estimation
```{r }
mod_spattemp <- sdmTMB( # should be running rather quickly
  data = dat,
  list(biomass ~ fyear,
       biomass ~ fyear),
  mesh = mesh,
  family = delta_lognormal(),
  offset = log(dat$areakmsqadj),
  spatial = list("on","on"),
  time = "year", 
  spatiotemporal = list("IID", "IID"),
  anisotropy = TRUE,
  share_range = TRUE,
  silent = TRUE
)

```

### Calculate residuals for each model predictor
```{r }
# FIX ME: can be improved by MCMC sampling instead of assuming multivariate distribution
mod_spattemp$data$resids <- residuals(mod_spattemp, type = "mle-mvn", 
                                      model = 1)
mod_spattemp$data$resids2 <- residuals(mod_spattemp, type = "mle-mvn", 
                                       model = 2)
```

and plot their density by year
```{r }
# binomial
ggplot(data=mod_spattemp$data, aes(x=resids, group=fyear, fill=fyear)) +
  geom_density(adjust=1.5, alpha=.4)

# lognormal
ggplot(data=mod_spattemp$data, aes(x=resids2, group=fyear, fill=fyear)) +
  geom_density(adjust=1.5, alpha=.4)

```

### Make year-specific spatial weights lists of sampling points by model component

The key difference between the predictor-based functions is that I remove the 
NAs from the lognormal model residuals before creating the spatial weights 
lists. The NA residuals represent pairs of points where whiting has not been 
present. Since the lognormal model prediction only estimates for present catches 
(with biomass > 0), we can exclude these for the autocorrelation metrics. 

```{r }
knw_spattemp_binom <- make_kn_dist_obj_binom(coords = mod_spattemp$data)
knw_spattemp_pos <- make_kn_dist_obj_pos(coords = mod_spattemp$data)

# inspect outcome
#knw_spattemp_binom$y2003

```

### Calculate year-specific Global Moran's I

The Global Moran's I measures the average level of spatial autocorrelation
across all samples. We apply the test for each year, allowing us to estimate
the annual average spatial correlation score I, and whether this score is
statistically significant. Moran's I is a cross-product between a variable and
its spatial lag, values from neighbouring locations, where a variable is 
expressed as its deviation from its mean (Cliff and Ord, 1981), 
where $\bar{x}$ represents the mean of an observation x, evaluated for 
locations $i$ and $j$. $w_{ij}$ represents spatial weights, and 
$\frac{n}{\sum_{i}\sum_{j} w_{ij}}$ is a normalisation term on the sum of 
spatial weights ${\sum_{i}\sum_{j} w_{ij}}$. This normalisation term removes 
dependence on the spatial weights and ensures that equal probability across
values (null hypothesis). 

$$
I = \frac{n}{\sum_{i}\sum_{j} w_{ij}}
    \frac{\sum_{i}\sum_{j} w_{ij}(x_i - \bar{x})(x_j - \bar{x})}
         {\sum_{i} (x_i - \bar{x})^2}
$$
The *spdep* package allows two applications of tests of spatial autocorrelation:
an analytical (theoretical) and a permutation (simulation-based) approach.  

The analytical approach operates under a null hypothesis of spatial randomness, 
and estimates the expected value and variance under probability theory. 
Statistical significance is then derived by comparing test statistics of to a 
(usually normal) reference distribution. 

The permutation-based approach builds a reference distribution by iteratively 
and randomly permuting values from the actual observations across locations. 
This process generates an exact null distribution conditional to the sample, 
preserving tests error rates even if data are skewed.

As we see from the residual density plots above, the distributions are roughly
normal, and skewed in some years. Permutation tests are less sensible to 
violations of the underlying assumptions, and are therefore more robust in 
these situations. Furthermore, we have small to moderate sample sizes in each 
year which may amplify the effect of extreme values in each year. Thus, we 
proceed with permutation tests in both global and local autocorrelation.

```{r }

# Check sample size 
table(dat$fyear)

morans_spattemp_m1 <- map(knw_spattemp_binom, ~ list(
  #moran.test(.x[[1]]$coordsdat$resids, .x[[1]]$nblistw) # analytical
  moran.mc(.x[[1]]$coordsdat$resids, .x[[1]]$nblistw, nsim = 999) # permutation-based
))
morans_spattemp_m2 <- map(knw_spattemp_pos, ~ list(
  moran.mc(.x[[1]]$coordsdat$resids, .x[[1]]$nblistw, nsim = 999)
))


```


### Plot year-specific Global Moran's I

The Moran Scatter Plot (Anselin, 1996) plots the spatially lagged variable on 
the y-axis and the original variable on the x-axis.The regression slope 
corresponds to Moran's I. The plot aims to classify the nature of spatial 
autocorrelation into four quadrants. Since the plot is centered on the mean,
(of zero), values to the right are $x_i - \bar{x}$ > 0, and the left 
$x_i - \bar{x}$ < 0, or can simply be referred high and low. Upper-right and 
lower-left quadrants are associated with positive spatial autocorrelation 
(similar values at neighbouring locations), whereas upper-left and and 
lower-right reflect negative spatial autocorrelation (dissimilar values at 
neighbouring locations).

Since the plot includes row labels of the plotted values, we get a first insight
of how singular points contribute to global patterns in spatial 
similarity/dissimilarity. These effects can be estimated using Local Indicators
of Spatial Autocorrelation (LISA), and are explained in the sections below. 

```{r }
# Function to plot global Moran's for both model components

globm_plot_fun <- function(moran_data, model_comp = c(1, 2)) {
  
  if (1 %in% model_comp) {
  xname <- "resids"
  p <- ggplot(moran_data, aes(x=x, y=wx)) + 
    geom_point(shape=1, size = 0.8) + 
    geom_smooth(formula=y ~ x, method="lm", linewidth = 0.2) + 
    geom_hline(yintercept=mean(moran_data$wx), lty=2) + 
    geom_vline(xintercept=mean(moran_data$x), lty=2) + 
    #theme_minimal() + 
    cowplot::theme_cowplot() +
    theme(plot.margin = margin(-1, -1, -1, -1),
          aspect.ratio = 1,
          axis.title = element_text(size = 9),
          axis.text = element_text(size = 8)) +
    geom_point(data=moran_data[moran_data$is_inf,], aes(x=x, y=wx), 
               shape=9, size = 0.8) +
    geom_text(data=moran_data[moran_data$is_inf,], 
              aes(x=x, y=wx, label=labels), vjust=1.5 , size = 3) +
    xlab(xname) + ylab(paste0("Spatially lagged ", xname))
  
  return(p)
  }
  
  if (2 %in% model_comp) {
    xname <- "resids2"
    p <- ggplot(moran_data, aes(x=x, y=wx)) + 
      geom_point(shape=1, size = 0.8) + 
      geom_smooth(formula=y ~ x, method="lm", linewidth = 0.2) + 
      geom_hline(yintercept=mean(moran_data$wx), lty=2) + 
      geom_vline(xintercept=mean(moran_data$x), lty=2) + 
      #theme_minimal() + 
      cowplot::theme_cowplot() +
      theme(plot.margin = margin(-1, -1, -1, -1),
            aspect.ratio = 1,
            axis.title = element_text(size = 9),
            axis.text = element_text(size = 8)) +
      geom_point(data=moran_data[moran_data$is_inf,], aes(x=x, y=wx), 
                 shape=9, size = 0.8) +
      geom_text(data=moran_data[moran_data$is_inf,], 
                aes(x=x, y=wx, label=labels), vjust=1.5 , size = 3) +
      xlab(xname) + ylab(paste0("Spatially lagged ", xname))
    
    return(p)
  }

}


```

Here, we apply the function to the model residuals and adjust the layout 
across the grid (in case we want to save it for posterity). 

```{r }

## We are demonstrating this function for the binomial (first) model component
# Make a list of Moran plots
morans_spattemp_m1_plots <- purrr::map(knw_spattemp_binom, ~ 
                                         moran.plot(.x[[1]]$coordsdat$resids, 
                                                    .x[[1]]$nblistw, 
                                                    return_df = TRUE # returns data
                                                    )
)
# Unfortunately, we cannot directly save the plots
# So, we need to use the plot-ready data and buld our own plots 
morans_spattemp_m1_gg <- purrr::map(morans_spattemp_m1_plots, ~ globm_plot_fun(
  moran_data = .x,
  model_comp = 1
))
# Arrange plots onto a grid for final output
globmorans_spattemp_m1_grid <- cowplot::plot_grid(
  plotlist = morans_spattemp_m1_gg,
  align = "hv", axis = "tb")
# Improve formatting to save output for own records
buffered_spattemp_m1_grid <- cowplot::ggdraw() +
  cowplot::draw_plot(globmorans_spattemp_m1_grid, 
                     x = 0.05, y = 0.05, width = 0.9, height = 0.9)


```

### Local indicators of spatial autocorrelation

While the Global Moran's I tells us if there is generally autocorrelation 
present, it does not tell which areas are similar/dissimilar. LISA (Local 
Indicators of Spatial Autocorrelation) decompose spatial autocorrelation into 
spatial units across the data set. Common examples (and demonstrated here) 
include local supplements to existing test such as Local Moran's Ii and Local 
Getis Ord Gi.

### Calculate year-specific Local Moran's Ii

Local Moran's Ii is estimated via 




```{r }

# Functions to calculate local autocorrelation (Moran) by model component

make_local_morans_obj_binom <- function(.x) {
  # Calculate conditional Local Moran's and adjust p-values
  locm_p <- localmoran_perm(.x[[1]]$coordsdat$resids, .x[[1]]$nblistw, 
                            nsim = 999, iseed = 123)
  .x[[1]]$coordsdat <- cbind(.x[[1]]$coordsdat, locm_p[, c("Ii", "E.Ii", 
                                                           "Var.Ii", "Z.Ii",
                                                           "Pr(z != E(Ii))",
                                                           "Pr(z != E(Ii)) Sim")
  ])
  .x[[1]]$coordsdat$locm_p_pv <- p.adjust(locm_p[, "Pr(z != E(Ii)) Sim"],
                                          "fdr")
  .x[[1]]$coordsdat$locm_significance <- ifelse(.x[[1]]$coordsdat$locm_p_pv <= 0.01, 
                                                print("sig"), print("insig"))
  
  # Get quadrant for hotspots
  .x[[1]]$coordsdat$quad_mean <- attr(locm_p, "quadr")$mean 
  locm_dat <- .x[[1]]$coordsdat
  return(locm_dat)
}

make_local_morans_obj_pos <- function(.x) {
  # Calculate conditional Local Moran's and adjust p-values
  locm_p <- localmoran_perm(.x[[1]]$coordsdat$resids2, .x[[1]]$nblistw, 
                            nsim = 999, iseed = 123)
  .x[[1]]$coordsdat <- cbind(.x[[1]]$coordsdat, locm_p[, c("Ii", "E.Ii", 
                                                           "Var.Ii", "Z.Ii",
                                                           "Pr(z != E(Ii))",
                                                           "Pr(z != E(Ii)) Sim")
  ])
  .x[[1]]$coordsdat$locm_p_pv <- p.adjust(locm_p[, "Pr(z != E(Ii)) Sim"],
                                          "fdr")
  .x[[1]]$coordsdat$locm_significance <- ifelse(.x[[1]]$coordsdat$locm_p_pv <= 0.01, 
                                                print("sig"), print("insig"))
  
  # Get quadrant for hotspots
  .x[[1]]$coordsdat$quad_mean <- attr(locm_p, "quadr")$mean 
  locm_dat <- .x[[1]]$coordsdat
  return(locm_dat)
}

# Function to check for significance among locations
check_psig_locm <- function(x) {
  pv <- x |>
    subset(select = "Pr(z != E(Ii)) Sim", drop = TRUE) 
  
  # checks significance for different approaches to adjust p-values
  # Note: Bonferroni is generally considered the most conservative
  pva <- function(pv) cbind("none" = pv, 
                          "FDR" = p.adjust(pv, "fdr"), "BY" = p.adjust(pv, "BY"),
                          "Bonferroni" = p.adjust(pv, "bonferroni"))
  pvsp <- pva(pv)
  
  #f <- function(x) sum(x < 0.005) # choose 0.005 as "interesting" alpha threshold
  f <- function(x) sum(x < 0.01)
  check <- apply(pvsp, 2, f)
  return(check)
}




```

The Local Moran's Ii provides a local autocorrelation score and quadrants....

Since we are testing a multidue of localities, i.e. survey sampling stations,
we need to consider adjusting the p-value. Furthermore, permutation tests are 
highly relevant here, once again as we sample multiple stations and analytical 
solution can be inapporrite if assumtions are not fulfilled .....

```{r }

## Demonstrate of binomial model component
# Calculate Local Moran's Ii
locm_spattemp_binom <- purrr::map(knw_spattemp_binom, 
                                  make_local_morans_obj_binom)
locm_spattemp_binom_df <- do.call(rbind, locm_spattemp_binom)


# Check for significance amongst all entries

locm_spattemp_binom_sig <- purrr::map(locm_spattemp_binom, ~ check_psig_locm(.x))


```

### Plot year-specific Local Moran's Ii

```{r }

# Function to format plots

locm_plot_fun <- function(full_obj, ire, coords, hull, Ii) {
  ggplot() +
    scale_fill_gradient2(
      low = "blue",
      mid = "white",
      high = "red",
      midpoint = 0  # Center of your scale
    ) +
    #scale_fill_viridis_c() + 
    geom_sf(data = full_obj, aes(fill = .data[[Ii]])) +
    geom_sf(data = ire, colour = "grey45", fill = "grey45") +
    geom_sf(data = coords, colour = "black", size = 0.001) +
    #geom_sf(data = coords, aes(shape = .data[[locm_significance]]), 
    #        colour = "black", size = 0.5) +
    #scale_shape_manual(values = c(1, 19)) +
    geom_sf(data = hull, colour = "black", fill = NA) +
    theme(
      legend.box.spacing = unit(1, "mm"),
      legend.key.width = unit(0.5, "mm"),
      legend.key.height = unit(1.5, "mm"),
      legend.spacing = unit(1, "mm"),
      legend.title = element_text(size = 4),
      legend.text = element_text(size = 3),
      legend.margin = margin(-1, 1, -1, -1),
      plot.margin = margin(-1, -1, -1, -1),
      aspect.ratio = 1,
      axis.text = element_blank(), 
      axis.ticks = element_blank()
    ) #+
  #labs(shape = "Significance", fill = "Local Moran's I")
  #labs(fill = "Local Moran's I")
}


```


```{r }

## Demonstrate of binomial model component
# Creates list of plots
all_locm_plots_base_binom <- purrr::map(h_v_spattemp_binom, ~ locm_plot_fun(
  full_obj = .x$full_obj,
  ire      = .x$ire,
  coords   = .x$coords,
  hull     = .x$hull,
  Ii = "Ii"
))

# Arrange listed plots on a grid
locm_plots_base_binom <- cowplot::plot_grid(plotlist = all_locm_plots_base_binom)
cowplot::save_plot(paste0(path, "fits/0/","locm_plots_base_binom.jpg"), 
          locm_plots_base_binom, base_asp = 1.6)



```



### Calculate year-specific Local Getis Ord Gi

singular entries of localised spatial autocorrelation can be difficult to 
interpret - this where the local Getis Ord Gi becomes relevant. 
It estimates hotspots of similarity that are convenient for both plotting and 
interpretation.

and Local 
Getis Ord Gi.

```{r }

# Functions to calculate local autocorrelation (Getis Ord) by model component

make_getis_ord_obj_binom <- function(.x) {
  # Calculate conditional Getis-Ord and adjust p-values
  locg_p <- localG_perm(.x[[1]]$coordsdat$resids, .x[[1]]$nblistw, 
                        nsim = 999, iseed = 123)
  locg_p_df <- attr(locg_p, "internals")
  .x[[1]]$coordsdat <- cbind(.x[[1]]$coordsdat, locg_p_df[, c("Gi", "E.Gi", 
                                                              "Var.Gi", "StdDev.Gi",
                                                              "Pr(z != E(Gi))",
                                                              "Pr(z != E(Gi)) Sim")
  ])
  
  .x[[1]]$coordsdat$locg_p_pv <- p.adjust(locg_p_df[, "Pr(z != E(Gi)) Sim"],
                                          "fdr")
  .x[[1]]$coordsdat$locg_significance <- ifelse(.x[[1]]$coordsdat$locg_p_pv <= 0.01, 
                                                print("sig"), print("insig"))
  
  # Get hotspot clusters
  locg_p_clust <- attr(locg_p, "cluster")
  .x[[1]]$coordsdat <- cbind(.x[[1]]$coordsdat, locg_p_clust)
  
  locg_dat <- .x[[1]]$coordsdat
  return(locg_dat)
}

make_getis_ord_obj_pos <- function(.x) {
  # Calculate conditional Getis-Ord and adjust p-values
  dat <- .x[[1]]$coordsdat
  locg_p <- localG_perm(dat$resids2, .x[[1]]$nblistw, 
                        nsim = 999, iseed = 123)
  locg_p_df <- attr(locg_p, "internals")
  dat <- cbind(dat, locg_p_df[, c("Gi", "E.Gi", "Var.Gi", "StdDev.Gi",
                                  "Pr(z != E(Gi))", "Pr(z != E(Gi)) Sim")
  ])
  
  dat$locg_p_pv <- p.adjust(locg_p_df[, "Pr(z != E(Gi)) Sim"],
                                          "fdr")
  dat$locg_significance <- ifelse(dat$locg_p_pv <= 0.01, 
                                                print("sig"), print("insig"))
  
  # Get hotspot clusters
  locg_p_clust <- attr(locg_p, "cluster")
  dat <- cbind(dat, locg_p_clust)
  
  locg_dat <- dat
  return(locg_dat)
}


# Function to check for significance among locations
check_psig_locg <- function(x) {
  pv <- x |>
    subset(select = "Pr(z != E(Gi)) Sim", drop = TRUE) 
  
  # checks significance for different approaches to adjust p-values
  # Note: Bonferroni is generally considered the most conservative
  pva <- function(pv) cbind("none" = pv, 
                            "FDR" = p.adjust(pv, "fdr"), "BY" = p.adjust(pv, "BY"),
                            "Bonferroni" = p.adjust(pv, "bonferroni"))
  pvsp <- pva(pv)
  
  #f <- function(x) sum(x < 0.005) # choose 0.005 as "interesting" alpha threshold
  f <- function(x) sum(x < 0.01)
  check <- apply(pvsp, 2, f)
  return(check)
}

```




```{r }

## Demonstrate of binomial model component
# Calculate Loncal Moran's Ii
getisord_spattemp_binom <- purrr::map(knw_spattemp_binom, make_getis_ord_obj_binom)
getisord_spattemp_binom_df <- do.call(rbind, getisord_spattemp_binom)





```




### Plot year-specific Local Getis Ord Gi

```{r }

# Function to plot test statistic Gi
locg_plot_fun <- function(full_obj, ire, coords, hull, Gi) {
  ggplot() +
    scale_fill_gradient2(
      low = "blue",
      mid = "white",
      high = "red",
      midpoint = 0  # Center of your scale
    ) +
    #scale_fill_viridis_c() + 
    geom_sf(data = full_obj, aes(fill = .data[[Gi]])) +
    geom_sf(data = ire, colour = "grey45", fill = "grey45") +
    geom_sf(data = coords, colour = "black", size = 0.001) +
    #geom_sf(data = coords, aes(shape = .data[[locg_significance]]), 
    #        colour = "black", size = 0.5) +
    #scale_shape_manual(values = c(1, 19)) +
    geom_sf(data = hull, colour = "black", fill = NA) +
    theme(
      legend.box.spacing = unit(1, "mm"),
      legend.key.width = unit(0.5, "mm"),
      legend.key.height = unit(1.5, "mm"),
      legend.spacing = unit(1, "mm"),
      legend.title = element_text(size = 4),
      legend.text = element_text(size = 3),
      legend.margin = margin(-1, 1, -1, -1),
      plot.margin = margin(-1, -1, -1, -1),
      aspect.ratio = 1,
      axis.text = element_blank(), 
      axis.ticks = element_blank()
      #  legend.position = c(.09, .85),
      #  legend.background = element_rect(linetype="solid", colour = "black")
      #legend.justification = c("left", "top")#,
      #legend.box.just = "left",
      #legend.margin = margin(2, 2, 2, 2)
    ) #+
  #labs(fill = "Getis-Ord G")
}

# Function to plot Getis ord hotspots
locg_hotspot_fun <- function(full_obj, ire, coords, hull, locg_p_clust) {
  ggplot() +
    scale_fill_manual(values = c("blue", "red")) +
    #scale_fill_viridis_c() + 
    geom_sf(data = full_obj, aes(fill = .data[[locg_p_clust]])) +
    geom_sf(data = ire, colour = "grey45", fill = "grey45") +
    geom_sf(data = coords, colour = "black", size = 0.001) +
    #geom_sf(data = coords, aes(shape = .data[[locg_significance]]), 
    #        colour = "black", size = 0.5) +
    #scale_shape_manual(values = c(1, 19)) +
    geom_sf(data = hull, colour = "black", fill = NA) +
    theme(
      legend.box.spacing = unit(1, "mm"),
      legend.key.width = unit(0.5, "mm"),
      legend.key.height = unit(1.5, "mm"),
      legend.spacing = unit(1, "mm"),
      legend.title = element_text(size = 4),
      legend.text = element_text(size = 3),
      legend.margin = margin(-1, 1, -1, -1),
      plot.margin = margin(-1, -1, -1, -1),
      aspect.ratio = 1,
      axis.text = element_blank(), 
      axis.ticks = element_blank())
}



```





```{r }

## Demonstrate of binomial model component
# Plotting Gi test statistic
all_locg_plots_base_binom <- purrr::map(h_v_spattemp_binom, ~ locg_plot_fun(
  full_obj = .x$full_obj,
  ire      = .x$ire,
  coords   = .x$coords,
  hull     = .x$hull,
  Gi = "Gi"
))
gord_plots_base_binom <- cowplot::plot_grid(plotlist = all_locg_plots_base_binom)
cowplot::save_plot(paste0(path, "fits/0/", "getis_ord_plots_base_binom.jpg"), 
                   gord_plots_base_binom, base_asp = 1.6)


# Plotting local hotspots of similarity/dissimilarity
all_locg_hotspot_plots_base_binom <- purrr::map(h_v_spattemp_binom, ~ locg_hotspot_fun(
  full_obj = .x$full_obj,
  ire      = .x$ire,
  coords   = .x$coords,
  hull     = .x$hull,
  locg_p_clust = "locg_p_clust"
))
hotspot_plots_base_binom <- cowplot::plot_grid(plotlist = all_locg_hotspot_plots_base_binom)
cowplot::save_plot(paste0(path, "fits/0/","getis_ord_hotspot_plots_base_binom.jpg"), 
                   hotspot_plots_base_binom, base_asp = 1.6)

```


```{r }


```


```{r }


```


```{r }


```

# References

Anselin, Luc. 1996. “The Moran Scatterplot as an ESDA Tool to Assess Local 
Instability in Spatial Association.” In Spatial Analytical Perspectives on GIS 
in Environmental and Socio-Economic Sciences, edited by Manfred Fischer, 
Henk Scholten, and David Unwin, 111–25. London: Taylor; Francis.

Cliff, Andrew, and J. Keith Ord. 1973. Spatial Autocorrelation. London: Pion.

Cliff AD, Ord JK (1981) Spatial processes. Pion, London

Moran, Patrick A. P. 1948. “The Interpretation of Statistical Maps.” 
Journal of the Royal Statistical Society, B 10: 243–51.





































